\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-26 tex/overview.tex
explain quantity that gives relative contribution of SCCs to robustness

Since both numerator and denominator are linear in the variables $k_i$ over which we are optimizing, an elementary argument shows the quantity will assume its minimum value at one of the vertices of the simplex.
The value at the $i$-th vertex equals
\begin{equation}\label{eq:robqual}
 q_i =
 \frac{2 d_i (1 - R_i)}
      {(k_i - 1) v_i^2 + 2 d_i},
\end{equation}
hence the network which maximizes robustness will have as many SCCs as possible be of the type which have the smallest value of $q_i$.

>>>>

Since both numerator and denominator are linear in the variables $k_i$ over which we are optimizing, an elementary argument shows the quantity will assume its minimum value at one of the vertices of the simplex.
The value at the $i$-th vertex equals
\begin{equation}\label{eq:robqual}
 q_i =
 \frac{2 d_i (1 - R_i)}
      {(k_i - 1) v_i^2 + 2 d_i},
\end{equation}
hence the network that maximizes robustness will have as many SCCs as possible be of the type which have the smallest value of $q_i$. For the SCC consisting of a single node that has a link connecting to itself $\lim_{N \rightarrow \infty} Nq = 1$. For other SCCs of two and three nodes this quantity is computed in \refsupp{} \ref{tab:structstabmat} and \ref{tab:structstabmat3}.

### 2015-07-26 tex/table2x2stab.tex
explain quantity that gives relative contribution of SCCs to robustness

\begin{table*}[h]
\begin{center}
\begin{tabular}{ c || c | c | c | c | c }
\hline
matrix & \specialcell{number\\of SCCs} & connectivity & \specialcell{dynamical \\ robustness} & \specialcell{probability\\of stability} & \specialcell{q \\ (\ref{eq:robqual})}\\
\hline
  $\begin{pmatrix}
a & b \\
d & c
\end{pmatrix}$ & 1 & 4 & 0.62 & 0.25 & 1.52\\
  $\begin{pmatrix}
a & b \\
d & 0
\end{pmatrix}$, $\begin{pmatrix}
0 & b \\
d & c
\end{pmatrix}$ & 1 & 3 & 0.5 & 0.25 & 1.5\\
  $\begin{pmatrix}
a & 0 \\
d & c
\end{pmatrix}$, $\begin{pmatrix}
a & b \\
0 & c
\end{pmatrix}$ & 2 & 3 & 0.67 & 0.25 & \\
$\begin{pmatrix}
a & 0 \\
0 & c
\end{pmatrix}$ & 2 & 2 & 0.5 & 0.25 & \\
\end{tabular}
\end{center}
\caption{{\bf Dynamical robustness and probability of stability for two variable systems derived analytically}. All matrices not listed have $0$ probability of stability.}\label{tab:structstabmat}
\end{table*}
% \twocolumn

>>>>

\begin{table*}[h]
\begin{center}
\begin{tabular}{ c || c | c | c | c | c }
\hline
matrix & \specialcell{number\\of SCCs} & connectivity & \specialcell{dynamical \\ robustness} & \specialcell{probability\\of stability} & \specialcell{$\lim_{N \rightarrow \infty} Nq$ \\ (\ref{eq:robqual})}\\
\hline
  $\begin{pmatrix}
a & b \\
d & c
\end{pmatrix}$ & 1 & 4 & 0.62 & 0.25 & 1.52\\
  $\begin{pmatrix}
a & b \\
d & 0
\end{pmatrix}$, $\begin{pmatrix}
0 & b \\
d & c
\end{pmatrix}$ & 1 & 3 & 0.5 & 0.25 & 1.5\\
  $\begin{pmatrix}
a & 0 \\
d & c
\end{pmatrix}$, $\begin{pmatrix}
a & b \\
0 & c
\end{pmatrix}$ & 2 & 3 & 0.67 & 0.25 & \\
$\begin{pmatrix}
a & 0 \\
0 & c
\end{pmatrix}$ & 2 & 2 & 0.5 & 0.25 & \\
\end{tabular}
\end{center}
\caption{{\bf Dynamical robustness and probability of stability for two variable systems derived analytically}. All matrices not listed have $0$ probability of stability.}\label{tab:structstabmat}
\end{table*}
% \twocolumn
